---
title: "London Locations"
author: "George WIllis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(ggmap)
```

```{r Load data, include=FALSE, echo=FALSE}
devtools::install_github("tlorusso/traveltime")

# load packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, purrr, sf, mapview, traveltime)

# how far can you go by public transport within 30 minutes?
traveltime_Tom <- traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.498848,-0.014388),
               traveltime=2100,
               type="public_transport",
               departure="2023-01-15T07:30:00")
traveltime_Elliott <- traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.5050744, -0.0897987),
               traveltime=2100,
               type="public_transport",
               departure="2023-01-15T07:30:00")
traveltime_George <- traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.512381397690866, -0.11643173685673865),
               traveltime=2100,
               type="public_transport",
               departure="2023-01-15T07:30:00")

```
All of us for 35 minutes travel time. Pretty clear map actually.

## Best locations to live based on work travel times

This is a very basic overview of all travel times for our respective station. For our locations the time is 35 minutes..

```{r Basic overview, echo=F, message=F}
m1 = mapview(traveltime_Elliott,  col.regions = c("grey"))
m2 = mapview(traveltime_George,  col.regions = c("pink"))
m1 + m2 + traveltime_Tom
```

## Modes of transport

This section will divide the travel time by type of travel for each location. First, Tom.

*Note: I can't split overground and underground unfortunately*

```{r LB methods of transport, echo=F, message=F}
traveltimes_Tom <-c("walking","cycling","bus","public_transport") %>%
  map(.,~traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.504573,-0.086054),
               traveltime=2400,
               type=.x,
               departure="2023-01-15T07:30:00") %>%
        mutate(mode=.x))

# map_dfr does not work well with sf objects (yet?) so we just..

# ... rbind the dataframes together via do.call
df_LB<-do.call(rbind.data.frame, traveltimes_Tom)

library(ggmap)
library(leaflet)

#get basemap with ggmap
basemap <- get_stamenmap(bbox = unname(st_bbox(df_LB)),maptype = "toner-hybrid")

#plot
ggmap(basemap)+
  geom_sf(data=df_LB,inherit.aes = FALSE, aes(fill=mode), alpha=0.5,color=NA)+
  scale_fill_viridis_d()+
  theme_void()+
  coord_sf(datum = NA)+
  facet_wrap(~mode)+
  guides(fill="none")+
  theme(plot.title=element_text(face="bold"),
        plot.subtitle=element_text(size = 10, margin=margin(t=5, b = 10)), 
        strip.text=element_text(face="bold",margin=margin(b = 4)))+
  labs(title="Traveltimemap", subtitle="Times from Tom",         caption="data : traveltimeplatform.com")
```

Now, George.

```{r WL methods of transport, echo=F, message=F}
traveltimes_George <-c("walking","cycling","bus","public_transport") %>%
  map(.,~traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.5031653,-0.11230509999995775),
               traveltime=1500,
               type=.x,
               departure="2023-01-15T07:30:00") %>%
        mutate(mode=.x))

# map_dfr does not work well with sf objects (yet?) so we just..

# ... rbind the dataframes together via do.call
df_WL<-do.call(rbind.data.frame, traveltimes_George)


#get basemap with ggmap
basemap <- get_stamenmap(bbox = unname(st_bbox(df_WL)),maptype = "toner-hybrid")

#plot
ggmap(basemap)+
  geom_sf(data=df_WL,inherit.aes = FALSE, aes(fill=mode), alpha=0.5,color=NA)+
  scale_fill_viridis_d()+
  theme_void()+
  coord_sf(datum = NA)+
  facet_wrap(~mode)+
  guides(fill="none")+
  theme(plot.title=element_text(face="bold"),
        plot.subtitle=element_text(size = 10, margin=margin(t=5, b = 10)), 
        strip.text=element_text(face="bold",margin=margin(b = 4)))+
  labs(title="Traveltimemap", subtitle="Times from George",         caption="data : traveltimeplatform.com")
```

And finally Elliott.

```{r LV methods of transport, echo=F, message=F}
traveltimes_Elliott <-c("walking","cycling","bus","public_transport") %>%
  map(.,~traveltime_map(appId="0ac98a50",
               apiKey="1a97779905179095dee3c98d35c972d0",
               location=c(51.49521,-0.143898),
               traveltime=1500,
               type=.x,
               departure="2023-01-15T07:30:00") %>%
        mutate(mode=.x))

# map_dfr does not work well with sf objects (yet?) so we just..

# ... rbind the dataframes together via do.call
df_LV<-do.call(rbind.data.frame, traveltimes_Elliott)


#get basemap with ggmap
basemap <- get_stamenmap(bbox = unname(st_bbox(df_LV)),maptype = "toner-hybrid")

#plot
ggmap(basemap)+
  geom_sf(data=df_LV,inherit.aes = FALSE, aes(fill=mode), alpha=0.5,color=NA)+
  scale_fill_viridis_d()+
  theme_void()+
  coord_sf(datum = NA)+
  facet_wrap(~mode)+
  guides(fill="none")+
  theme(plot.title=element_text(face="bold"),
        plot.subtitle=element_text(size = 10, margin=margin(t=5, b = 10)), 
        strip.text=element_text(face="bold",margin=margin(b = 4)))+
  labs(title="Traveltimemap", subtitle="Times from Elliott",         caption="data : traveltimeplatform.com")
```

## Overlap

This finds the common ground between all three locations.

```{r Overlaps, echo=F, message=F}
overlap <- st_union(traveltime_Tom, traveltime_Elliott)
#m4 = mapview(overlap,  col.regions = c("green"), alpha.regions = 0.2)
stations <- read_csv("data/stations.csv")
stations_sf <- st_as_sf(stations, coords=c("Longitude","Latitude"), crs=4326)
stations_overlap <- st_intersection(stations_sf, overlap)

m4 <- mapview(stations_overlap, zcol = "Name", label=("Line"), legend = F) + mapview(overlap, col.regions = c("green"), alpha.regions = 0.2)
m4
```

